\Sof{TBA - New Titles in the comments}

### 2020-04-20 paper/icsme20.tex
paper update

$1031$ security patches. $539$ of these patches are identified with Common Weakness
Enumeration IDs (CWE). In Table~\ref{tab:patterns}, the most prevailing categories are presented. To satisfy the Wilcoxon test size requirement, types of vulnerabilities
with less than $20$ instances were merged in a bigger group named \textit{Miscellaneous}.

\begin{table}[h]
\scriptsize
	\caption{Guidelines to produce maintainable code}
\begin{tabular}{L{1.1cm}L{2.1cm}L{4.3cm}}

\toprule
\textbf{Pattern} & \textbf{Name} & \textbf{Description}\\
\midrule

\textbf{CWE-89} & 
 Improper Neutralization of Special Elements used in an SQL Command/SQL Injection (23 cases) & 
 When developers do not keep untrusted data
     separate from SQL queries. If an attacker sends a command that
     exploits the syntax of the SQL interpreter, then SQL injection attack is possible.\\\midrule

\textbf{CWE-611} & 
 Improper Restriction of XML External Entity Reference (24 cases) & 
	XML documents are exchanged through the web containing entities with URIs
 	that resolve to local/external files. Thus, when XML parsers are not well configured,
 	attackers have allowed to directly those files.\\\midrule

 \textbf{CWE-20} & 
 Improper Input Validation (76 cases) & 
	When developers
 	forget to validate the inputs of an application, attackers may have control
 	of the control/data flow of the program.\\\midrule

  \textbf{CWE-200} & 
Information Exposure (39 cases)& 
Application's logs are one way of intentional/unintentional disclosure information
 	to attackers. Many times attackers get access to logs when sould not be authorized to.\\\midrule

   \textbf{CWE-352} & 
Cross-Site Request Forgery/CSRF (22 cases)& 
Poor session tokens generation
     and management usually allow attackers to send forged HTTP requests
     including authentication information from the victim to the vulnerable web
     application.\\\midrule

       \textbf{CWE-264} & 
Permissions, Privileges, and Access Controls (59 cases)& 
Incorrectly
 	    implemented functionalities related to authentication and session
 	    management, allowing an attacker to gain access to session tokens,
 	    passwords, keys, and other sensitive data.\\\midrule

 	           \textbf{CWE-399} & 
Resource Management Errors (22 cases)& 
Resource management issues are found more frequently
 		in programming languages that do not manage memory automatically (e.g., C/C++
 	    and Objective-C), i.e., where developers are responsible for
 	    handling it instead. It is one of the main causes of Denial-of-Service attacks.\\\midrule

 	     	           \textbf{CWE-79} & 
Improper Neutralization of Input During Web Page Generation/Cross-site Scripting (63 cases)& 
Lack of proper validation or escaping
 	    allows attackers to submit untrusted data to web browsers through malicious
 	    scripts that can hijack the user sessions or redirect the user to malicious
 	    sites.\\\midrule

 	     	           \textbf{CWE-22} & 
Improper Limitation of a Pathname to a Restricted Directory/Path Traversal (37 cases) & 
When developers forget to neutralize special elements within the path names to files/directories, attackers
 	may leverage this flaw to resolve to a location outside of the restricted directory and gain access to documents
 	or entire repositories.\\\midrule

 	 	     	           \textbf{MISC} & 
Miscellaneous (666 cases) & 
This pattern comprises
 		several other security refactorings that do not have a CWE assigned and patterns that
 		do not satisfy the Wilcoxon test size requirement of more than $20$ refactorings.\\
\bottomrule
\end{tabular}
\label{tab:patterns}
\end{table}

@@

\subsection{Statistical Validation}\label{sec:statsval}
%
To validate the maintainability differences in different groups of commits
(e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank
test with the significance level $\alpha = 0.05$~\cite{10.2307/3001968}. In
other words, we test the null hypothesis that the maintainability difference
between pairs of versions $v_{s-1}$, $v_s$ (i.e., before and after a
security-commit) come from the same distribution. Nevertheless, this test has a
limitation: it does not consider the groups of commits with a zero-difference
maintainability. In $1959$, Pratt provided an improvement to the test to solve
this issue making the test more robust. Thus, we use a version of the Wilcoxon
test that incorporates the cases where maintainability is different from zero~\cite{10.2307/2282543}.
To understand the effect-size, as
advocated by the Common-language effect sizes\cite{graw:1992}, we compute the
mean difference, the median of the difference, and the percentage of cases that
reduce maintainability.
%
\section{Results}\label{sec:results}

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.5\textwidth]{figures/main_per_guideline.pdf}
 	\caption{Impact of the security patches per guideline.}
	\label{fig:guidelines}
	\scalebox{0.5}{
	\begin{tabular}{r@{: }l r@{: }l}
	$WCC$ & Write Clean Code & $KACB$ & Keep Architecture Components Balanced\\
	$CACL$ & Couple Architecture Components Loosely & $SCM$ & Separate Concerns in Modules \\
	$KUIS$ & Keep Unit Interfaces Small & $WCO$ & Write Code Once \\
	$WSimpleUC$ & Write Simple Units of Code & $WShortUC$ & Write Short Units of Code
	\end{tabular}
	}
\end{figure}

Maintainability is being calculated as the mean of the guidelines computed
by BCH. Figure~\ref{fig:guidelines} shows the impact of security patches on each 
guideline individually. 
For each type of
guideline, three types of impact of patches in the software maintainability
are presented: \emph{negative}, maintainability decreases (\emph{red});
\emph{none}, maintainability remains the same (\emph{yellow}); and,
\emph{positive}, maintainability increases (\emph{green}). Next to each
type of guideline, it is shown the mean ($\overline{x}$) and median (M)
of the maintainability difference and the p-value resulting from the
Paired Wilcoxon signed-rank test.

Regarding the impact of security patches for each guideline, we observe
that overall patches have a significant positive impact in $5$ guidelines: 
\emph{Write Clean Code} (p-value = $4.9$x$10^{-54}$), \emph{Keep Architecture 
Components Balanced} (p-value = $5.26$x$10^{-71}$), \emph{Couple Architecture 
Components Loosely} (p-value = $2.43$x$10^{-07}$), \emph{Keep Unit Interfaces 
Small} (p-value = $2.25$x$10^{-13}$), \emph{ Write Code Once} (p-value = 
$7.9$x$10^{-35}$). However, for each of these guidelines we also observe a 
substantial number of cases where the maintainability suffers a negative 
impact $-$ from $10\%$ to $35\%$ $-$ which highlights the need of better 
practices/techniques/tools to produce software. \emph{Separate Concerns in Module} 
guideline also follows the same results but without any statistical 
significance since the p-value is higher than $0.05$. According to the 
results, \emph{Write Simple Units of Code} (p-value=$0.015$ and $38.2\%$/$396$ 
of negative cases) and \emph{Write Short Units of Code} (p-value=$0.029$ and 
$38.3\%$/$397$ of negative cases) are the most affected affected guidelines.

>>>>

$1031$ security patches. $912$ of these patches are identified with Common Weakness
Enumeration IDs (CWE) where $59.1\%$ were scraped from the National Vulnerability Dataset (NVD) and the remaining $40.9\%$ were manually classified following the \texttt{Research Concepts} view map from the CWE's list.

% In Table~\ref{tab:patterns}, the most prevailing categories are presented. To satisfy the Wilcoxon test size requirement, types of vulnerabilities
% with less than $20$ instances were merged in a bigger group named \textit{Miscellaneous}.

% \begin{table}[h]
% \scriptsize
% 	\caption{Guidelines to produce maintainable code}
% \begin{tabular}{L{1.1cm}L{2.1cm}L{4.3cm}}
%
% \toprule
% \textbf{Pattern} & \textbf{Name} & \textbf{Description}\\
% \midrule
%
% \textbf{CWE-89} &
%  Improper Neutralization of Special Elements used in an SQL Command/SQL Injection (23 cases) &
%  When developers do not keep untrusted data
%      separate from SQL queries. If an attacker sends a command that
%      exploits the syntax of the SQL interpreter, then SQL injection attack is possible.\\\midrule
%
% \textbf{CWE-611} &
%  Improper Restriction of XML External Entity Reference (24 cases) &
% 	XML documents are exchanged through the web containing entities with URIs
%  	that resolve to local/external files. Thus, when XML parsers are not well configured,
%  	attackers have allowed to directly those files.\\\midrule
%
%  \textbf{CWE-20} &
%  Improper Input Validation (76 cases) &
% 	When developers
%  	forget to validate the inputs of an application, attackers may have control
%  	of the control/data flow of the program.\\\midrule
%
%   \textbf{CWE-200} &
% Information Exposure (39 cases)&
% Application's logs are one way of intentional/unintentional disclosure information
%  	to attackers. Many times attackers get access to logs when sould not be authorized to.\\\midrule
%
%    \textbf{CWE-352} &
% Cross-Site Request Forgery/CSRF (22 cases)&
% Poor session tokens generation
%      and management usually allow attackers to send forged HTTP requests
%      including authentication information from the victim to the vulnerable web
%      application.\\\midrule
%
%        \textbf{CWE-264} &
% Permissions, Privileges, and Access Controls (59 cases)&
% Incorrectly
%  	    implemented functionalities related to authentication and session
%  	    management, allowing an attacker to gain access to session tokens,
%  	    passwords, keys, and other sensitive data.\\\midrule
%
%  	           \textbf{CWE-399} &
% Resource Management Errors (22 cases)&
% Resource management issues are found more frequently
%  		in programming languages that do not manage memory automatically (e.g., C/C++
%  	    and Objective-C), i.e., where developers are responsible for
%  	    handling it instead. It is one of the main causes of Denial-of-Service attacks.\\\midrule
%
%  	     	           \textbf{CWE-79} &
% Improper Neutralization of Input During Web Page Generation/Cross-site Scripting (63 cases)&
% Lack of proper validation or escaping
%  	    allows attackers to submit untrusted data to web browsers through malicious
%  	    scripts that can hijack the user sessions or redirect the user to malicious
%  	    sites.\\\midrule
%
%  	     	           \textbf{CWE-22} &
% Improper Limitation of a Pathname to a Restricted Directory/Path Traversal (37 cases) &
% When developers forget to neutralize special elements within the path names to files/directories, attackers
%  	may leverage this flaw to resolve to a location outside of the restricted directory and gain access to documents
%  	or entire repositories.\\\midrule
%
%  	 	     	           \textbf{MISC} &
% Miscellaneous (666 cases) &
% This pattern comprises
%  		several other security refactorings that do not have a CWE assigned and patterns that
%  		do not satisfy the Wilcoxon test size requirement of more than $20$ refactorings.\\
% \bottomrule
% \end{tabular}
% \label{tab:patterns}
% \end{table}

@@

\subsection{Statistical Validation}\label{sec:statsval}
%
To validate the maintainability differences in different groups of commits
(e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank
test with the significance level $\alpha = 0.05$~\cite{10.2307/3001968}. In
other words, we test the null hypothesis that the maintainability difference
between pairs of versions $v_{s-1}$, $v_s$ (i.e., before and after a
security-commit) come from the same distribution. Nevertheless, this test has a
limitation: it does not consider the groups of commits with a zero-difference
maintainability. In $1959$, Pratt provided an improvement to the test to solve
this issue making the test more robust. Thus, we use a version of the Wilcoxon
test that incorporates the cases where maintainability is different from zero~\cite{10.2307/2282543}.
The Wilcoxon test requires a distribution size of at leat $20$ instances.
To understand the effect-size, as
advocated by the Common-language effect sizes\cite{graw:1992}, we compute the
mean difference, the median of the difference, and the percentage of cases that
reduce maintainability.
%
\section{Results}\label{sec:results}

@@

\begin{figure}[h]
 	\centering
	\vspace{-0.3 cm}
 	\includegraphics[width=0.45\textwidth]{figures/main_per_guideline.pdf}
	\vspace{-0.3 cm}
 	\caption{Impact of the security patches per guideline.}
	\label{fig:guidelines}
	\vspace{0.2 cm}
	\scalebox{0.5}{
	\begin{tabular}{r@{: }l r@{: }l}
	$WCC$ & Write Clean Code & $KACB$ & Keep Architecture Components Balanced\\
	$CACL$ & Couple Architecture Components Loosely & $SCM$ & Separate Concerns in Modules \\
	$KUIS$ & Keep Unit Interfaces Small & $WCO$ & Write Code Once \\
	$WSimpleUC$ & Write Simple Units of Code & $WShortUC$ & Write Short Units of Code
	\end{tabular}
	}	
\end{figure}

Maintainability is being calculated as the mean of the guidelines computed
by BCH. Figure~\ref{fig:guidelines} shows the impact of security patches on each 
guideline individually. For each type of
guideline, three types of impact of patches in the software maintainability
are presented: \emph{negative}, maintainability decreases (\emph{red});
\emph{none}, maintainability remains the same (\emph{yellow}); and,
\emph{positive}, maintainability increases (\emph{green}). Next to each
type of guideline, it is presented the mean ($\overline{x}$) and median (M)
of the maintainability difference and the p-value resulting from the
Paired Wilcoxon signed-rank test.

Regarding the impact of security patches for each guideline, we observe
that overall patches have a significant positive impact in $6$ guidelines: 
\emph{Write Clean Code} (p-value = $4.9$x$10^{-54}$), \emph{Keep Architecture 
Components Balanced} (p-value = $5.26$x$10^{-71}$), \emph{Couple Architecture 
Components Loosely} (p-value = $2.43$x$10^{-07}$), \emph{Keep Unit Interfaces 
Small} (p-value = $2.25$x$10^{-13}$), \emph{ Write Code Once} (p-value = 
$7.9$x$10^{-35}$). However, for each of these guidelines we also observe a 
substantial number of cases where the maintainability suffers a negative 
impact $-$ from $10\%$ to $35\%$ $-$ which highlights the need of better 
practices/techniques/tools to produce software. \emph{Separate Concerns in Module} 
guideline also follows the same results but without any statistical 
significance since the p-value is higher than $0.05$. According to the 
results, \emph{Write Simple Units of Code} (p-value=$0.015$ and $38.2\%$/$396$ 
of negative cases) and \emph{Write Short Units of Code} (p-value=$0.029$ and 
$38.3\%$/$397$ of negative cases) are the most affected affected guidelines.

 %%%%%%%%%%% HERE
